An agent-based model of interdisciplinary interactions in science\\%\medskip }

### 2020-05-25 Docs/Rochebrune2018/rochebrune.tex
.

\title{An Agent-based Model of Interdisciplinary Interactions\\\medskip
\textit{Ecole thématique de Rochebrune 2018\\
Proposition de Communication
}
}
\author{\noun{Juste Raimbault}$^{1,2}$\\
$^{1}$ UMR CNRS 8504 Géographie-cités\\
$^{2}$ UMR-T IFSTTAR 9403 LVMT
}
\date{}

@@

\begin{abstract}
	This paper introduces a parcimonious agent-based model of interdisciplinary relationships in collective entreprises of knowledge discovery. Under simple behavioral assumptions, we show that individual choices influence the distribution of compromise points between emergent level of disciplinary depth and interdisciplinarity, in a non-linear way. We claim that independently of each research subject, the organization of research, and more particularly the local balancing between vertical and horizontal research, strongly influence the final positioning of research results and the extent of the knowledge front, what suggests direct implications for research policies.
\end{abstract}

@@

Akerlof, G. A., & Michaillat, P. (2018). Persistence of false paradigms in low-power sciences. Proceedings of the National Academy of Sciences, 201816454.

@@

Pluchino, A., Biondo, A. E., & Rapisarda, A. (2018). Talent Versus Luck: The Role Of Randomness In Success And Failure. Advances in Complex Systems, 21(03n04), 1850014.

>>>>

\title{An agent-based model of interdisciplinary interactions in science\\%\medskip
%\textit{Ecole thématique de Rochebrune 2018\\
%Proposition de Communication
}
}
\author{\noun{Juste Raimbault}$^{1,2}$\\
$^{1}$ UMR CNRS 8504 Géographie-cités\\
$^{2}$ UMR-T IFSTTAR 9403 LVMT
}
\date{}

@@

\begin{abstract}
An increased interdisciplinarity in science projects has been highlighted as crucial to tackle complex real-world challenges, but also as beneficial for the development of disciplines themselves. This paper introduces a parcimonious agent-based model of interdisciplinary relationships in collective entreprises of knowledge discovery, to investigate the impact of scientist-level decisions and preferences on global interdisciplinarity patterns. Under the assumption of simple rules for individual researcher project management, such as trade-offs between invested time overhead and knowledge benefit, model simulations show that individual choices influence the distribution of compromise points between emergent level of disciplinary depth and interdisciplinarity in a non-linear way. Different structures for collaboration networks also yield various outcomes in terms of global interdisciplinarity. We conclude that independently of the research field, the organization of research, and more particularly the local balancing between vertical and horizontal research, already influences the final positioning of research results and the extent of the knowledge front. This suggests direct applications to research policies with a bottom-up leverage on the interactions between disciplines.
\end{abstract}

\cite{Hofstra9284} diversity/innovation

\cite{Ellemers7561}: applied persp?

\cite{brown_murray_furlong_coco_dablander_2020}

\cite{2019arXiv191003628T} maintsream / interdisc papers

\cite{jang2019coevolutionary} abm structure knowledge coevol

https://journals.plos.org/plosone/article/citation?id=10.1371/journal.pone.0221907 : assymetry of interdisc

https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.3000065

importance of teams vs solo authors Pavlidis, I., Petersen, A. M., \& Semendeferi, I. (2014). Together we stand. Nature Physics, 10(10), 700.

https://www.nature.com/articles/s41467-019-11401-8

VANVLOKHOVEN2019751 : model for oa and research quality

@@

Akerlof, G. A., \& Michaillat, P. (2018). Persistence of false paradigms in low-power sciences. Proceedings of the National Academy of Sciences, 201816454.

@@

Pluchino, A., Biondo, A. E., \& Rapisarda, A. (2018). Talent Versus Luck: The Role Of Randomness In Success And Failure. Advances in Complex Systems, 21(03n04), 1850014.
